---
title: "conditionals_loops"
author: "Karol Paya"
format: html
editor_options: 
  chunk_output_type: console
---
```{r}
library("stringr")
```

```{r}
pm2_5<-300

if (pm2_5 <100) {
  print("Unhealthy for sensitive groups")
} else if (pm2_5 >= 100 && pm2_5 < 150) {
  print("Unhealthy for sensitive groups")
} else (pm2_5>150)
  print ("Health risk present")

```



```{r}
species<-"blue whale"


if (str_detect(species,pattern="whale")) {
  print("You found a whale!")
} else {
#print nothing
}
  
```


Store the base price of a burrito as base_burrito with a value of 6.50. Store main_ingredient with a starting string of “veggie.” Write a statement that will return the price of a burrito based on what a user specifies as “main_ingredient” (either “veggie”, “chicken” or “steak”) given the following:

A veggie burrito is the cost of a base burrito
A chicken burrito costs 3.00 more than a base burrito
A steak burrito costs 3.25 more than a base burrito

```{r}
base_burrito<-6.5
main_ingredient<-"veggie"

if (main_ingredient=="veggie") {
  price<-base_burrito
  print(price)
} else if (main_ingredient=="chicken") {
  price<-base_burrito*3
  print(price)
} else if (main_ingredient=="steak") {
  price<-base_burrito*3.25
  print(price)
} else {
  }
```

```{r}

```

