---
title: "conditionals_loops"
author: "Karol Paya"
format: html
editor_options: 
  chunk_output_type: console
---
```{r}
library("stringr")
```

```{r}
pm2_5<-10

if (pm2_5 <100) {
  print("Unhealthy for sensitive groups")
} else if (pm2_5 >= 100 && pm2_5 < 150) {
  print("Unhealthy for sensitive groups")
} else (pm2_5>150)
  print ("Health risk present")

```



```{r}
species<-"blue whale"


if (str_detect(species,pattern="whale")) {
  print("You found a whale!")
} else {
#print nothing
}
  
```


Store the base price of a burrito as base_burrito with a value of 6.50. Store main_ingredient with a starting string of “veggie.” Write a statement that will return the price of a burrito based on what a user specifies as “main_ingredient” (either “veggie”, “chicken” or “steak”) given the following:

A veggie burrito is the cost of a base burrito
A chicken burrito costs 3.00 more than a base burrito
A steak burrito costs 3.25 more than a base burrito

```{r}
base_burrito<-6.5
main_ingredient<-"veggie"

if (main_ingredient=="veggie") {
  price<-base_burrito
  print(price)
} else if (main_ingredient=="chicken") {
  price<-base_burrito*3
  print(price)
} else {
  price<-base_burrito*3.25
  print(price)
} 
```

Create a new vector called fish that contains the values 8, 10, 12, 23 representing counts of different fish types in a fish tank (goldfish, tetras, guppies, and mollies, respectively). Write a for loop that iterates through fish, and returns what proportion of total fish in the tank are that species. Assume that these counts represent all fish in the tank.
```{r}
fish<-c(8,10,12,23)
for (i in fish) {
  proportion=i/sum(fish)
  print(proportion)
  }
```

There is an existing vector in R called month.name that contains all month names (just ry running month.name in the Console to check it out). Write a for loop that iterates over all months in month.name and prints “January is month 1,” “February is month 2”, etc.
```{r}
counter=1
for (i in month.name){
  print (paste(i, "is month",counter))
  counter=counter+1
}
```



